Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
small

The second analyser, named cost-reduction, works along a different
axis: It tries to find the 
triple pattern that, if cached, would provide the greatest cost
benefit. To do so, it will rerun the query planner on the incoming
query while simulating that the results of a certain triple pattern
was in the cache. The simulation will run for \emph{all} triple
patterns that do not already have a cached result. If the cost
reduction of the best plan is larger than a certain limit, the
prefetcher is invoked.

>>>>

The second analyser, named cost-reduction, works along a different
axis: It will find the 
triple pattern that, if cached, would provide the greatest cost
benefit. To do so, it will rerun the query planner on the incoming
query while simulating that the results of a certain triple pattern
was in the cache. The simulation will run for \emph{all} triple
patterns that do not already have a cached result. If the cost
reduction of the best plan is larger than a certain limit, the
prefetcher is invoked.
